---
title: "Practical Machine Learning Project"
author: "Yunpeng Zhan"
date: "Augest 05, 2018"
output:
  html_document: default
  pdf_document: default
---

# Scenario

Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement - a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset).  

The goal of the project is to predict the manner in which they did the exercise.

# Data

The training data for this project are available here: [https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv]

The test data are available here: [https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv]

The data for this project come from this source: [http://groupware.les.inf.puc-rio.br/har]. If you use the document you create for this class for any purpose please cite them as they have been very generous in allowing their data to be used for this kind of assignment.

# Code and resutls

## Load required library and set seed.

``` {r}
library(caret)
library(rpart)
library(rpart.plot)
library(randomForest)
set.seed(1234)
```

## Load datasets and premary cleaning

``` {r}
trainingurl <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
testingurl <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
if(!file.exists("data")) {dir.create("data")}
download.file(trainingurl, destfile = "./data/pml-training.csv")
download.file (testingurl, destfile = "./data/pml-testing.csv")
trainingdata <- read.csv("./data/pml-training.csv", na.strings=c("NA","#DIV/0!", ""))
testdata <- read.csv("./data/pml-testing.csv", na.strings=c("NA","#DIV/0!", ""))

# Remove columns that are all Nulls

trainingdata<-trainingdata[,colSums(is.na(trainingdata)) == 0]
testdata <-testdata[,colSums(is.na(testdata)) == 0]

# Remove unrelated variables

trainingdata <- trainingdata[,-c(1:7)]
testdata <-testdata[,-c(1:7)]
```

## Partitioning the training data set to allow cross-validation

``` {r}
subs <- createDataPartition(y=trainingdata$classe, p=0.75, list=FALSE)
subtraining <- trainingdata[subs, ] 
subtesting <- trainingdata[-subs, ]
```

## First model -- Decision Tree

``` {r}
model <- rpart(classe ~ ., data=subtraining, method="class")
rpart.plot(model, main="Classification Tree")
prediction1 <- predict(model, subtesting, type = "class")
confusionMatrix(prediction1, subtesting$classe)
```

## Second Model -- Random Forest

``` {r}
model2 <- randomForest(classe ~. , data=subtraining, method="class")
prediction2 <- predict(model2, subtesting, type = "class")
confusionMatrix(prediction2, subtesting$classe)
```

** From the results, it is obvious that Random Forest model performed better whose accuracy is 0.995 while the other one is 0,727.

## Make prediction based on the Random Forest model

``` {r}
predictfinal <- predict(model2, testdata, type="class")
predictfinal
```
